Static contract checking for Haskell

### 2011-12-21 paper/paper.tex
Paper: improved description of phi_injective.

\subsection{$\ttrans{}$ -- Datatypes}
We break down the translation for datatypes in four parts, described in figure~\ref{ktrans}
$$\ttrans{\mbox{data } T = K_1~a_1, \dots, K_n~a_n} = \phi_\text{injective} \land \phi_\text{disjoint} \land \phi_\text{cf} \land \phi_\text{lazy}$$

\begin{itemize}
\item $(\phi_\text{injective})$ Constructors are injective.  That is, for
  each term constructor $K$,
  if $K e_1 \cdots e_n = K e'_1 \cdots e'_n$, then $e_i = e'_i$ for
  all $i$.  We axiomitize this via projections $\proj{i}{K}$: for each $i$,
  $\proj{i}{K}(K e_1 \cdots e_n) = e_i$.
\item $(\phi_\text{disjoint})$ Distinct constructors have disjoint ranges.
\item $(\phi_\text{cf})$ Then, we have to give crash-freeness conditions for each $K_i$:
  Notice that we have a equivalence.
  \begin{itemize}
  \item $\gets$: if we pack crash-free values in a data constructor,
    the resulting value is crash-free.  If $K$ has arity $n$
    then we assert $\ctrans{K \in \cfc^n \to \cfc}^-$.

>>>>

\subsection{$\ttrans{}$ -- Datatypes}
We break down the translation for datatypes in four parts, described in Figure~\ref{ktrans}
$$\ttrans{\mbox{data } T = K_1~a_1, \dots, K_n~a_n} = \phi_\text{injective} \land \phi_\text{disjoint} \land \phi_\text{cf} \land \phi_\text{lazy}$$

\begin{itemize}
\item $(\phi_\text{injective})$ Constructors are injective.  That is,
  for each term constructor $K$, if $K e_1 \cdots e_n = K e'_1 \cdots
  e'_n$, then $e_i = e'_i$ for all $i$.  We axiomitize this via
  projections $\proj{i}{K}$: for each $i$, $\proj{i}{K}(K e_1 \cdots
  e_n) = e_i$.  NB: unlike for user defined functions, the $\min{}$
  constraint on unfolding projections is on the \emph{argument}, and
  not the \emph{function application} itself.  I.e., instead of
  $\min{\proj{i}{K}(K e_1 \cdots e_n)}$ we have $\min{K e_1 \cdots
    e_n}$.  We guard with the latter, not the former, because the
  primary purpose of projectors is to axiomitize the injectivity of
  constructors.  E.g., given $S~x_1 = S~x_2$, and $\min{S~x_1}$, we
  want to conclude that $x_1 = x_2$.  We won't, in general, have
  $\min{\proj{1}{S}(S~x_1)}$ here, so such a min-constraint would
  block us.

  We also use projectors in some versions of the case-expression
  translation, to Skolemize, but this is just a happy coincidence.  In
  particular, user programs will never contain explicit projections.
  If a user wants to project they need to write a projection function
  using pattern matching.
\item $(\phi_\text{disjoint})$ Distinct term constructors have
  disjoint ranges.  Note that we don't axiomitize disjointness of term
  constructors from distinct \emph{data types}.
\item $(\phi_\text{cf})$ Then, we have to give crash-freeness conditions for each $K_i$:
  Notice that we have a equivalence.
  \begin{itemize}
  \item $\gets$: if we pack crash-free values in a data constructor,
    the resulting value is crash-free.  If $K$ has arity $n$
    then we assert $\ctrans{K \in \cfc^n \to \cfc}^-$.
